Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Fix code example

\begin{quote}
\small
\begin{verbatim}
spec = do
  describe "List as a Monoid" $ do
    describe "mempty" $ do
      it "is a left identity" $ property $ \x ->
        mempty <> x == x

      it "is a right identity" $ property $ \x ->
        x <> mempty == x

    describe "<>" $ do
      it "is associative" $ property $ \x y z ->
        (x <> y) <> z == x <> (y <> z)
\end{verbatim}
\end{quote}

>>>>

\begin{quote}
\small
\begin{verbatim}
spec = do
  describe "List as a Monoid" $ do
    describe "mempty" $ do
      it "is a left identity" $ property $ \x ->
        mempty <> x == (x :: [Int])

      it "is a right identity" $ property $ \x ->
        x <> mempty == (x :: [Int])

    describe "<>" $ do
      it "is associative" $ property $ \x y z ->
        (x <> y) <> z == (x <> (y <> z) :: [Int])
\end{verbatim}
\end{quote}
